\documentclass[10pt, a4paper]{article}

\input{cover-letter-themes/theme_selection}

%----------------------------------------------------------------------------------------
%	 THEMES
%----------------------------------------------------------------------------------------

% Define the desired theme out of the following: beige, blue, bw, coral, earth, framed, gray, minimal, onyx, plain
% See screenshots in preview/ directory
\theme{bw}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need a particular field, just remove the content leaving the command, e.g. \jobtitle{}

\name{Domagoj Karl} % Your name
\jobtitle{Software Engineer} % Job title/career
\location{Zagreb, Croatia} % Address/location
\phone{+385 97 791 0514} % Phone number
\mail{karl.domagoj@gmail.com} % Mail
\employerinfo{Hiring Manager's Name \\
912 Company Address \\
City, State Zip Code \\
517-444-6098 \\
hiring.manager@gmail.com} % Contact information of the employer. Make sure to end every row with "\\"

\begin{document}

\makeprofile % Print name & job description

\makecontact % Print defined contact information

\today % Command for inserting today's date.

\letterspace % Command for adding larger vertical space
\makeemployerinfo % Print employer contact information

Dear Mr./Ms. Lastname,

I am writing to express my interest in the Embedded Software Engineer position, as advertised. With a solid background in Linux Yocto development and extensive experience in designing, developing, and optimizing embedded systems for the automotive industry, I am excited about the opportunity to contribute to your dynamic Software team and help drive the innovation.
\\\\
During my tenure at Rimac Technology, I have honed my skills in designing and upholding Yocto Linux distributions for Infotainment ECUs, alongside developing Linux device drivers and optimizing system performance. My hands-on experience with custom-made hardware using Toradex-Apalis i.MX SoMs and NXP SoC has equipped me with a deep understanding of hardware-software interactions and the intricacies of embedded system development. Additionally, my proficiency in scripting languages such as Python and Bash, has enabled me to effectively manage software releases and provide live engineering support to customers.
\\\\
I am enthusiastic about the opportunity to bring my unique blend of technical skills, project experience, and collaborative mindset to the Embedded Software Engineer role. Thank you for considering my application. I look forward to the possibility of discussing how my qualifications align with the needs of your team.

%\lipsum[3][7-10] % Command to generate dummy text

%\begin{itemize}
%    \item \lipsum*[1][7-8]
%    \item \lipsum*[6][7-10]
%    \item \lipsum*[5][7-9]
%\end{itemize}

%\lipsum[12-13]

\letterspace
Sincerely,

\letterspace
{\name}

\end{document}
